Dark Control:\\ A Unified Account of Default Mode Function\\ by Control Theory and Reinforcement Learning

### 2017-04-06 paper/paper.tex
NEW FIG: neurobiogical implementation of RL in by the DMN
more

\subsection{Putting everything together}
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{rl_process_chart.pdf}
  \caption{The DMN as an RL agent... \textbf{Please add a figure caption}}
  \label{fig:rl_process_chart}
\end{figure}
The DMN is today known to consistently increase in neural
  activity when humans engage in goal-directed behavior that are detached from
  current sensory environment \citep{kenet2003spontaneously, fiser2004small}
  and it was proposed to be situated at the top of the functional network hierarchies
  \citep{carhart2010default, margulies2016situating}.
  Its involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the implicit computation of
  action and state cascades as a function of what happened in the past.
  A policy represents the repertoire of possible actions
    on the world given a current state. It encodes the probabilites of
    choosing actions to be executed in a certain situation.
% Interactions between external and internal sources of
%   information are probably commonplace during perception \citep{gershman2010learning}
The DMN may subserve
  constant exploration of possible future actions and their
  cumulative reward outcomes. Implicit computation of future choices
  provides an explanation for the
  evolutionary emergence and practical usefulness of mind-wandering
  in humans.

>>>>

\subsection{Putting everything together}
The DMN is today known to consistently increase in neural
  activity when humans engage in goal-directed behavior that are detached from
  current sensory environment \citep{kenet2003spontaneously, fiser2004small}
  and it was proposed to be situated at the top of the functional network hierarchies
  \citep{carhart2010default, margulies2016situating}.
  Its involvement in thinking about the past,
  the future, and hypothetical possibilities ties in with the implicit computation of
  action and state cascades as a function of what happened in the past.
  A policy represents the repertoire of possible actions
    on the world given a current state. It encodes the probabilites of
    choosing actions to be executed in a certain situation.
% Interactions between external and internal sources of
% information are probably commonplace during perception \citep{gershman2010learning}
\begin{figure}[!h]
  \includegraphics[width=.9\linewidth]{neurobiological_and_rl_overview_DMN.pdf}
  \caption{Neurobiological implementation of RL by the DMN...}
  \label{fig:rl_process_chart}
\end{figure}

The DMN may subserve
  constant exploration of possible future actions and their
  cumulative reward outcomes. Implicit computation of future choices
  provides an explanation for the
  evolutionary emergence and practical usefulness of mind-wandering
  in humans.
